D_exp_2

### 2018-08-11 experiments/D_exp_2/writeup/D_exp_2.Rmd
making D be like C

---
title: "Experiment 3 of 4"
author: "Matt Green"
output:
  html_document:
    toc: true
    <!--toc_float: true-->
    mathjax: default
    template: default
    code_folding: show
    theme: default
---  
<style>
table, th, td {
    border: 1px grey;
    border-collapse: collapse;
    padding:2px 5px 2px 5px
}  
</style>

# Experiment 3

```{r loadLibraries, message=FALSE}
library(knitr); library(MASS); library(ggplot2); library(lme4); library(xtable); library(plyr); library(lattice); library(LMERConvenienceFunctions); library(car); library(grid); library(lmerTest); library(reshape2); library(ggplot2); library(languageR); library(pander); source('summarySEwithin2.R'); library(Hmisc)
```

@@

```{r showInstructions, echo=FALSE, cache=TRUE}
v = c("crisp", "crisp", "vague", "vague")
n = c('number', 'number', 'number', 'number')
t = c("matching", "comparison", "matching", "comparison")
e = c("Choose a square with 6 dots", "Choose a square with fewer than 20 dots", "Choose a square with about 10 dots", "Choose a square with far fewer than 20 dots")
i = data.frame(v, n, t, e)
names(i) = c("vagueness", "instruction format", "selection task", "example instruction")
pander(i, justify=c('center', 'left', 'left', 'left'))
```

```{r showItems, echo=FALSE, cache=TRUE}
items = c(1,2,3,4,5,6,7,8)
i = data.frame(Item = c("1","2","3","4"),
               x = c("06:15:24", "16:25:34", "26:35:44", "36:45:54"))
names(i) = c('Item', 'Numbers of dots')
pander(i, justify=c('center', 'center'))
```

```{r getData, echo=T}
# data.txt
rawdata <- read.table('preprocessing/data_processed.txt', sep=' ')
```

```{r trimat25sd}
trimdata <- perSubjectTrim.fnc(rawdata, response='RT', subject='Subject', trim = 2.5)$data
rtdata <- trimdata
```

```{r rtplot1, fig.width=7, fig.height=3}
# this plot uses a precomputed summary done by summarySEwithin
# and data trimmed at 2.5 sd per subject
rtdataplot1 <- summarySEwithin2(data=perSubjectTrim.fnc(rawdata, response='RT', subject='Subject', trim = 2.5)$data,
                                measurevar="RT_log", withinvars=c("Vagueness", "Selection", "Item"), idvar="Subject")
dodge = position_dodge(width=0.2)
rtdataplot1$Condition <- as.factor(paste(sep=' ', rtdataplot1$Selection, rtdataplot1$Vagueness))
rtplot=ggplot(rtdataplot1,
              aes(y=RT_logNormed, x=Item, ymin=RT_logNormed-ci, ymax=RT_logNormed+ci,
                group=Condition, shape=Condition, fill=Condition)) +
  geom_line(position=dodge) +
  geom_errorbar(width=.2, position=dodge) +
  geom_point(size=2, position=dodge) +
  scale_shape_manual("",values = c(22, 22, 21, 21)) +
  scale_fill_manual("",values=c("black","white","black","white")) +
  ggtitle("Response time") +
  ylab("Respone time (log (ms))") + 
  xlab("") +
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        legend.key = element_blank(), aspect.ratio=1,
        axis.text.x = element_text(angle = 45, hjust = 1),
        plot.background=element_rect(fill=NA, color='white')) +
  facet_grid(~Selection) 
rtplot
```

```{r rtplotHmisc, fig.width=7, fig.height=3}
# n.b. rtdata has been trimmed at 2.5 sd: use rawdata if you want untrimmed data
rawdata$Condition <- as.factor(paste(sep=' ', rawdata$Selection, rawdata$Vagueness))
ggplot(rawdata, aes(y=RT_log, x=Item, group=Condition, shape=Condition, fill=Condition)) + 
  stat_summary(fun.data = "mean_cl_boot", position=position_dodge(0.2)) +
  scale_shape_manual("",values = c(22, 22, 21, 21)) +
  scale_fill_manual("",values=c("black","white","black","white")) +
  facet_grid(~Selection) +
  theme(
    panel.background=element_rect(fill=NA, color='black'),
    panel.grid.major=element_line(color='grey95'), 
        #panel.grid.minor = element_blank(),
        legend.key=element_blank(), 
        aspect.ratio=1,
        axis.text.x=element_text(angle = 45, hjust = 1)
        )
```

```{r rtlmer, cache=TRUE}
rtlmer = lmerTest::lmer(data=rtdata,
                        RT_log ~ c_Vag * c_Sel + c_Itm +
                          (1 + c_Vag * c_Sel + c_Itm | Subject))
```

```{r rtlmersummaryxtable, results='asis', cache=TRUE, echo=F}
print(xtable(summary(rtlmer)$coef, digits=c(0,2,2,1,1,4)),type='html')
```

```{r seplmersforcomparison, results='asis', cache=TRUE, echo=-3}
s1 <- subset(rtdata, subset=Selection=='Comparison')
s1lm <- lmerTest::lmer(data=s1, RT_log ~ c_Vag + c_Itm + (1 + c_Vag + c_Itm | Subject))
print(xtable(summary(s1lm)$coef, digits=c(0,2,2,1,1,4)), type='html')
```

```{r seplmersformatching, results='asis', cache=TRUE, echo=-3}
s2 <- subset(rtdata, subset=Selection=='Matching')
s2lm <- lmerTest::lmer(data=s2, RT_log ~ c_Vag + c_Itm + (1 + c_Vag + c_Itm | Subject))
print(xtable(summary(s2lm)$coef, digits=c(0,2,2,1,1,4)), type='html')
```

>>>>

---
title: "D_exp_2"
author: "Matt Green"
output:
  html_document:
    toc: true
    toc_float: false
---

```{r, echo=FALSE, message=FALSE}
library(knitr)
library(tidyverse)
library(broom)
library(broom.mixed)
library(lme4)
library(lmerTest)
library(dotwhisker)
library(kableExtra)
library(LMERConvenienceFunctions)
library(data.table)
library(gridExtra)
source("D_exp_2_functions/preprocessing.R")
source("D_exp_2_functions/pretty_coef_table.R")
source("D_exp_2_functions/summarySEwithin2.R")
root_dir <- getwd()
data_dir <- "D_exp_2_data"
```

```{r}
dat <- preprocessing(root_dir, data_dir)
dat <- perSubjectTrim.fnc(dat, response='RT', subject='Subject', trim = 2.5)$data
dat$RT_log <- log(dat$RT)
```

# Info and Procedure (Method)

@@

# Sample display

Remember to do a screenshot for the sample display.

# Full table of instructions

```{r, echo=FALSE}
instructions_table <- 
  dat %>%
    select(Item, Quantity, Vagueness, Selection, Instruction) %>%
    unique() %>%
    arrange(Item, Quantity, Vagueness, Selection) %>%
    spread(key=Vagueness, value=Instruction)
# kable(instructions_table, format="latex", booktabs = TRUE)
instructions_table %>% 
  kable(align='cccll', caption="Full table of instructions") %>% 
      kable_styling(full_width = F, position = "left", font_size = 11) 
```

# Means plots

```{r trimat25sd}
dat_plot <- summarySEwithin2(dat, measurevar="RT_log", withinvars=c("Vagueness", "Selection", "Item"), idvar="Subject")
```

```{r rtplot1, fig.width=7, fig.height=3}
dodge = position_dodge(width=0.2)
dat_plot$Condition <- as.factor(paste(sep=' ', dat_plot$Selection, dat_plot$Vagueness))
rtplot=ggplot(dat_plot,
              aes(y=RT_logNormed, x=Item, ymin=RT_logNormed-ci, ymax=RT_logNormed+ci,
                group=Condition, shape=Condition, fill=Condition)) +
  geom_line(position=dodge) +
  geom_errorbar(width=.2, position=dodge) +
  geom_point(size=2, position=dodge) +
  scale_shape_manual("",values = c(22, 22, 21, 21)) +
  scale_fill_manual("",values=c("black","white","black","white")) +
  ggtitle("Response time") +
  ylab("Respone time (log (ms))") + 
  xlab("") +
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        legend.key = element_blank(), aspect.ratio=1,
        axis.text.x = element_text(angle = 45, hjust = 1),
        plot.background=element_rect(fill=NA, color='white')) +
  facet_grid(~Selection) 
rtplot
```

```{r}
dat_borderline <- dat
```

```{r, "Borderline response distribution plot", fig.width=7, fig.height=3.5, echo=FALSE, results='hide'}
dat_borderline$response_cat <- factor(dat_borderline$response_cat, levels= c("Near", "Expected", "Far"))

ggplot(dat_borderline) + 
  geom_bar(aes(response_cat, group=Selection:Vagueness, fill=Vagueness), position=position_dodge(width=NULL)) +   
  scale_fill_grey() + 
  xlab(NULL) + 
  ggtitle('Borderline response distribution') + 
  facet_grid(~Selection) +
  theme_bw() + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), legend.key = element_blank(), legend.position="top", aspect.ratio=1, plot.background = element_rect(fill=NA, color='white'), strip.background=element_blank(), legend.key.size=unit(4, 'mm'), axis.text.x = element_text(angle = 15))

```

# Hypotheses

# Results

```{r rtlmer, cache=TRUE, results='asis'}
dat_model <- dat
dat_model$c_Vag <- ifelse(dat_model$Vagueness=="Crisp", -0.5, 0.5)
dat_model$c_Sel <- ifelse(dat_model$Selection=="Comparison", -0.5, 0.5)
dat_model$c_Itm <- ifelse(dat_model$Item=="06:15:24", -.75, ifelse(dat_model$Item=="16:25:34", -.25, ifelse(dat_model$Item=="26:35:44", .25, .75)))
rtlmer = lmerTest::lmer(data=dat_model,
                        RT_log ~ c_Vag * c_Sel + c_Itm +
                          (1 + c_Vag * c_Sel + c_Itm | Subject))
pretty_coef_table(rtlmer, "rtlmer")
```

```{r seplmersforcomparison, results='asis', cache=TRUE, echo=-5}
dat_model <- subset(dat, subset=Selection=='Comparison')
dat_model$c_Vag <- ifelse(dat_model$Vagueness=="Crisp", -0.5, 0.5)
dat_model$c_Itm <- ifelse(dat_model$Item=="06:15:24", -.75, ifelse(dat_model$Item=="16:25:34", -.25, ifelse(dat_model$Item=="26:35:44", .25, .75)))
s1lm <- lmerTest::lmer(data=dat_model, RT_log ~ c_Vag + c_Itm + (1 + c_Vag + c_Itm | Subject))
pretty_coef_table(s1lm, "s1lm")
```

```{r seplmersformatching, results='asis', cache=TRUE, echo=-5}
dat_model <- subset(dat, subset=Selection=='Matching')
dat_model$c_Vag <- ifelse(dat_model$Vagueness=="Crisp", -0.5, 0.5)
dat_model$c_Itm <- ifelse(dat_model$Item=="06:15:24", -.75, ifelse(dat_model$Item=="16:25:34", -.25, ifelse(dat_model$Item=="26:35:44", .25, .75)))
s2lm <- lmerTest::lmer(data=dat_model, RT_log ~ c_Vag + c_Itm + (1 + c_Vag + c_Itm | Subject))
pretty_coef_table(s2lm, "s2lm")
```

# Discussion
